Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-15 main.Rmd
cyclic calendar algebra multiple-to-single for quasi updated

The representation of single order-up quasi-circular granularities using multiple order-up quasi-circular granularities is not discussed in this paper and is left for future work.

<!-- as they promote the exploratory analysis through visualization. -->

@@

<!--The infrastructure of systematic exploration of observed variable across pair of cyclic time granularities has been implemented in the
R package `gravitas`. --> A missing piece is to enable user-defined temporal calendars and compute multiple order-up quasi-circular granularities from the hierarchy table. Also, computation of cyclic aperiodic granularities would require computing aperiodic linear granularities first. A few R packages like `almanac` and `gs` provide functionality to create recurring events that are not periodic. These functions can be imported in the `gravitas` package to accommodate for aperiodic cyclic granularities.

>>>>

<!-- CONTENT CHANGE -->
<!-- The representation of single order-up quasi-circular granularities using multiple order-up quasi-circular granularities is not discussed in this paper and is left for future work. -->

This case is similar to \ref{eq:multifromsingle-quasi2}. Single-order-up quasi-circular granularity ($C_{G_{l},G_{m'}}$) could be obtained from multiple-order-up quasi-circular granularity ($C_{G_l,G_{m}}$) and single/multiple order-up circular granularity $C_{m',m}$ using \ref{eq:multifromsingle-quasi2}.

\begin{equation} \label{eq:multifromsingle-quasi3}
\begin{split}
C_{G_{l},G_{m'}}(z) & = C_{G_l,G_{m}}(z) - \sum_{w=0}^{C_{m',m}(z) -1}(\vert T_{w} \vert)\\
\end{split}
\end{equation}

where, $T_w$ is such that $G_{m'}(w) = \bigcup_{z \in T_w}G_{l}$, $\vert T_w \vert$ is the cardinality of set $T_w$.
<!-- as they promote the exploratory analysis through visualization. -->

@@

<!--The infrastructure of systematic exploration of observed variable across pair of cyclic time granularities has been implemented in the
R package `gravitas`. --> A missing piece is to enable user-defined temporal calendars. Also, computation of cyclic aperiodic granularities would require computing aperiodic linear granularities first. A few R packages like `almanac` and `gs` provide functionality to create recurring events that are not periodic. These functions can be imported in the `gravitas` package to accommodate for aperiodic cyclic granularities.
